# Analysis Notes

Make sure to run make.R first and load the necessary objects.

```{r}

loadd(onc.dat)
loadd(cn.d.onc)

```

## Is the network similarity driven by abundance of lichen?

In a PerMANOVA with sequential partitioning of variance, we find that
genotype has a significant effect on network similarity (R2 = 0.54, p
= 0.030). When moved to the end of the model, the genotypic effect is
no longer significant (p = 0.11), and Bark Roughness (R2 = 0.26, p <
0.01) and Percent Cover (R2 = 0.10, p = 0.03) are both
significant. These results collectively support the hypothesis that
genetically based variation in bark roughness increases the cover of
lichens and leads to more similar lichen networks. Given that
Condensed Tannins, although genetically based (R2 = 0.32, p = 0.03),
do not significantly predict network similarity suggests that the
effect of Bark Roughness is structural rather than biochemically
mediated (e.g., through increased leaching of phytochemicals that
could impact lichen establishment and growth).

```{r}


    cn.geno.trait.pc  <- vegan::adonis2(
                                    cn.d.onc^(2)~ geno + CT + pH + CN + BR + PC,
                                    by = "term", 
                                    data = onc.dat, 
                                    mrank = TRUE,
                                    permutations = 100000)
    cn.trait.pc.geno  <- vegan::adonis2(
                                    cn.d.onc^(2)~ CT + pH + CN + BR + PC + geno,
                                    by = "term", 
                                    data = onc.dat, 
                                    mrank = TRUE,
                                    permutations = 100000)

```

# How does bark roughness affect the structure of the lichen networks? Is
it driven by lichen abudance (Percent Cover)?

Both Network Size (R2 = 0.87, p < 0.01) and Network Centralization (R2
= 0.05, p < 0.01) significantly explained the similarity of lichen
networks. These effects remained significant, even after variance
explained by Percent Cover was accounted for in the model. This
supports the conlcusion that the genetically based patterns in network
similarity are related to both the abundance of lichen and to other
factors that determine the structure of the networks. 

```{r}

    cn.l.cen.pc  <- vegan::adonis2(
                                     cn.d.onc~ L + Cen + PC,
                                     by = "term", 
                                     data = onc.dat, 
                                     mrank = TRUE,
                                     permutations = 100000)

    cn.pc.l.cen  <- vegan::adonis2(
                                     cn.d.onc~ PC + L + Cen,
                                     by = "term", 
                                     data = onc.dat, 
                                     mrank = TRUE,
                                     permutations = 100000)

```
