---
title: "Rock Lichen data from Sunset Crater"
author: M.K. Lau
output: pdf_document

---

# Analysis Summary

- Dead trees and non-lichen species were removed from lichen community
  analyses. 
- Lichen communities were adequately sampled, based on species
  accumulation curves, with moth resistant trees accumulating slightly
  more lichen species.
- Lichen communities (abundance, richness, diversity, composition)
were significantly, generally negatively, affected by moth
susceptibility.
- Several tree variables, including light availability, leaf litter
  abundance and rock abundance, were impacted by moth susceptibility.
- Analysis of causal pathways supported an indirect link between moth
  susceptibility and impacts on lichen communities via decreasing rock
  (i.e. habitat) availability through increased leaf abscission and
  accumulation on rocks under trees.
- These results support a genetically based link between intraspecific
  variation in susceptibility to an insect herbivore and community
  dynamics in an arid ecosystem.
- Given the possible impacts of cliimate change on this system, this
  study supports the conclusion that community and ecosystem impacts
  need to be considered in an evolutionary context.

```{r, echo = TRUE, results = "hide", eval = TRUE}
# 0. Supporting functions and libraries
## Support functions

dif <- function(x){
    out=x[1]
    for (i in 2:length(x)){
        out=out-x[i]
    }
    return(out)
}

## Libraries
my.libs <- c("vegan", "ecodist", "xtable")
if (any(!(my.libs %in% installed.packages()[, 1]))){
    sapply(my.libs[!(my.libs %in% installed.packages()[, 1])], 
           install.packages)
}else{}
sapply(my.libs, require, character.only = TRUE)


```

# Load Data


The following are variable descriptions (Variable, Type, Range, Definition):

    

- Moth,categorical,0 or 1,Was the tree susceptible (0) or resistant (1) to moth attack?
- Live/Dead,categorical,0 or 1,Was the tree dead (0) or alive (1)?
- Litter %,continuous,0 to 100,Percent cover inside quadrat
- Rocks > 3cm? %,continuous,0 to 100,Percent cover of rocks > 3cm? inside quadrat
- Rocks < 3cm? %,continuous,0 to 100,Percent cover of rocks < 3cm? inside quadrat
- Shrubs %,continuous,0 to 100,Percent cover of shrubs inside quadrat
- Grass %,continuous,0 to 100,Percent cover of grass inside quadrat
- Branches %,continuous,0 to 100,Percent cover of branches on ground inside quadrat
- Distance,continuous,0 to 100,"Distance from main trunk, converted to percent of crown radius at that azimuth"
- Azimuth,continuous,0 to 360,Compass direction from main trunk
- Slope,continuous,0 to 90,Topographical steepness
- Aspect,continuous,0 to 360,Compass direction of slope
- Light,continuous,,Amount of light available to epiliths

```{r results = "hide"}

## Data are in ../data/scrl
l.dat <- read.csv("../data/scrl/spp_env_combined.csv")

## Summary of data
summary(l.dat)

## remove dead trees
l.dat <- l.dat[l.dat[, "Live.Dead"] != 0, ]

## Lichen species list
spp.l <- c("Acacon", "Acasup", "Acaobp", "Sterile.sp", "Brown.cr",
"Lobalp", "Canros", "Calare", "Phydub", "Rhichr", "Xanlin", "Xanpli",
"Xanele", "GrBr.cr", "Gray.cr")
spp.moss <- c("Synrur", "Cerpur.Bryarg")

## Create a community matrix
com <- l.dat[, colnames(l.dat) %in% spp.l]
com.moss <- l.dat[, colnames(l.dat) %in% spp.moss]

## Add the tree labels to the rownames
rownames(com) <- paste(l.dat[, "Moth"], l.dat[, "Tree.pairs"], sep = "_")
rownames(com.moss) <- paste(l.dat[, "Moth"], l.dat[, "Tree.pairs"], sep = "_")
rownames(l.dat) <- paste(l.dat[, "Moth"], l.dat[, "Tree.pairs"], sep = "_")

```


# Species accumulation

Are the communities on each tree type adequately sampled?

```{r specacum}

spa.all <- specaccum(com)
spa.res <- specaccum(com[l.dat[, "Moth"] == 0, ])
spa.sus <- specaccum(com[l.dat[, "Moth"] == 1, ])

plot(spa.all,
     ylim = c(0, 20),
     xlab = "Cumulative Trees Sampled",
     ylab = "Lichen Species Observed")
lines(spa.res$sites, spa.res$richness, 
      ylim = c(0, 20), lty = 2, lwd = 3)
lines(spa.sus$sites, spa.sus$richness, 
      ylim = c(0, 20), lty = 3, lwd = 3)
legend("bottomright", 
       legend = c("All", "Resistant", "Susceptible"), 
       lty = c(1, 2, 3), lwd = c(1, 2, 2))

```

# Moth trees have different microenvironments 

- paired t-tests 

# Moth trees have different lichen communities (FIGURE ch.plot A, R, H) 

less abundant and diverse (paired t-tests, in text) 

```{R }
abun <- apply(com, 1, sum)
rich <- apply(com, 1, function(x) sum(sign(x)))
shan <- apply(com, 1, diversity, index = "shannon")
tt.a <- t.test(tapply(abun, l.dat[, "Tree.pairs"], diff))
tt.r <- t.test(tapply(rich, l.dat[, "Tree.pairs"], diff))
tt.h <- t.test(tapply(shan, l.dat[, "Tree.pairs"], diff))
tt.arh <- do.call(rbind, 
                  list(a = unlist(tt.a), r = unlist(tt.r), h = unlist(tt.h)))
data.frame(tt.arh)

```

composition is different (PERMANOVA, in text and supplement)

```{R, cache  = TRUE}

com.ds <- cbind(com, ds = rep(0.0001, nrow(com)))
set.seed(123)
ptab.moth <- adonis2(com.ds~ Moth, data = l.dat, 
                    strata = l.dat[, "Tree.pairs"], 
                    by = "margin", nperm = 100000)
xtable(ptab.moth)

```

three main species were reduced by moths (FDR paired t-tests, in text + supplement)

```{R}

ind.spp <- lapply(com, function(x, p) t.test(tapply(x, p, diff)), p = l.dat[, "Tree.pairs"])
isp <- apply(do.call(rbind, lapply(ind.spp, unlist)), 2, as.numeric)
rownames(isp) <- names(ind.spp)
isp[, "p.value"] <- p.adjust(isp[, "p.value"], method = "fdr")
isp <- isp[order(isp[, "p.value"]), ]
head(isp[, 1:3])

```

# Litter covering rocks was the main driver (FIGURE = ORDINATION)

light not litter predicted lichen composition (PERMANOVA, table 3, Ordination)

```{R, cache = TRUE}

set.seed(123)
ptab.env <- adonis2(com.ds ~  Light...average + Litter.., data = l.dat, 
                   strata = l.dat[, "Tree.pairs"],  
                   by = "margin", nperm = 100000)
xtable(ptab.env)
```

```{R ord-com-plot, cache = TRUE, width = 5, height = 5, dpi = 400}

nmds.out <- nmds(vegdist(com.ds), 2, 2)
ord <- nmds.min(nmds.out, dims = 2)
ord.pch <- c("R", "S")[(l.dat[, "Moth"] + 1)]
plot(X2~ X1, data = ord, pch = ord.pch)

```

litter not light was correlated with large rocks (dist cor, in text)

```{R}

cor.test(tapply(l.dat[, "Big.rocks.."], l.dat[, "Tree.pairs"], diff),
         tapply(l.dat[, "Litter.."], l.dat[, "Tree.pairs"], diff))
cor.test(tapply(l.dat[, "Big.rocks.."], l.dat[, "Tree.pairs"], diff),
         tapply(l.dat[, "Light...average"], l.dat[, "Tree.pairs"], diff))

```

